Rising from the Ashes II.: something something

### 2024-09-02 paper/ms.tex
another one

The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, and, of course, enrichment models. Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible. However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.

>>>>

The \MgFe{} value of star forming gas is the result of a complicated mixture of many different aspects of the TNG model, to name a few: stellar and AGN feedback which alter gas inflows and outflows, secular, dynamical evolution, SF prescription, magnetic fields, (lack of) cosmic rays, diffusivity of hydrodynamics solver, and, of course, enrichment models. Isolating the cause of the ``incorrect'' \MgFe{} vs time evolution at high-$z$\footnote{Our case study of a single galaxy is hardly cause to firmly assert that the fiducial evolution is incorrect.} is not straightforward nor, in our opinion, even possible. However, we do offer one reasonable explanation -- the SFE at the high densities more present at high-$z$ is too low.
